%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% !TeX program = lualatex
% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}
\usepackage{lmodern}
% For mathematical symbols
\usepackage{amsmath}
\usepackage{url}
\usepackage[svgnames]{xcolor}
\usepackage[colorlinks=true, linkcolor=Maroon, urlcolor=Maroon, citecolor=blue]{hyperref}
\usepackage[symbol]{footmisc}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\usepackage[backend=biber,sorting=none]{biblatex}
\addbibresource{main.bib}

% Set applicant's personal data for header
\name{Saurabh Khanduja}
\roles{\textcolor{steelblue}{\textbullet} Computer Vision Engineer \textcolor{steelblue}{\textbullet} Backend Engineer}
\email{khandujasaurabh@gmail.com}
\github{https://github.com/saurabheights}
\portfolio{https://saurabheights.github.io/}
\linkedin{https://linkedin.com/in/saurabheights}
\scholar{https://tinyurl.com/yc62fvb7}
\phone{+49 1772075019}
\address{Aalstrasse 3, Kaiserslautern, Germany - 67655}
\contacts{}
\stackoverflow{https://stackoverflow.com/users/1874627/saurabheights}


\begin{document}
    % Print the header
    \makeheader
    
    \begin{cvsection}[\faInfinity]{Summary}
    \textit{Computer Vision and Machine Learning specialist with expertise in real-time multi-camera multi-object tracking, object re-identification, and robust software engineering.
    }
    \end{cvsection}
    
    % work experience
    \begin{cvsection}[\faBriefcase]{Professional Experience}
        \begin{cvsubsection}{ML Engineer\rightarrow Head of Perception}{Ikara Vision Systems Gmbh}{Sept 2021 -- July 2025}
        \vspace{0.25em}
        \textit{Multi-Camera Multi-Person Tracking (Terraform, Docker, Python, PyTorch, AWS (S3, EC2 \& IAM),  Pandas, MMLabs, Optuna)}  
        \begin{itemize}
            \item Developed real-time multi-camera tracking across 50+ synchronized cameras for secure site monitoring.  
            \item Enhanced multi-camera joins using pose triangulation (RTMPose) and appearance embeddings (Clip-ReID).  
            \item Improved re-identification pipeline, achieving 55\% improvement in mAP over Clip-ReID baseline (40\% \rightarrow 62\%).
            \item In-house built tools for Multi-Camera Labeling, Visualization and Analysis.
            \item \textbf{AutoLabel++}: A scalable framework to train object detection models to new sites using knowledge distillation.
        \end{itemize}
        \vspace{-0.3em}   % reduce space above
        
        \begin{center}
        \rule{0.5\linewidth}{0.4pt}  % half-width line
        \end{center}
        \vspace{-0.3em}   % reduce space below
        
        \textit{ Distributed Computer Vision solutions for Customer Behavioral Analysis (Docker, Python, Celery, Ansible, Mongo, PostgreSQL, InfluxDB, TensorRT, Rabbitmq, Telegraf, Grafana, Jira, SQLite)}
            \begin{itemize}
                \item \textbf{Core Responsibility} - Took ownership of a mismanaged third-party project with over 30K lines-of-code and deployed across 1,000+ stores in 3 countries.
                \item Led team of 7 engineers to demystify the monolithic application, introduced structure to undocumented processes, resolved high volumes of client complaints, and restored product stability and client confidence.
                \item Redesigned high demand components of application from a centralized management server to a distributed management system.
                \item Redesign periodic polling with event-driven push, reducing read requests by $\sim$94\%.
                \item Reviewed over 20K LOC and implemented unit and integration testing followed with continuous integration pipelines to uncover inherent bugs and ensure long-term product robustness and stability.
                \item Achieved a complete 100\% resolution of client complaints related to software (non-ML) issues.
                \item Improved the core computer vision product with state of the art models and tracking algorithm tuned to specific sites using anonymized feed collection and automated labeling with human-in-the-loop.
                \item Successfully deployed solutions across 1000+ stores using a cost-effective in-house deployment manager.
            \end{itemize}
        
        \vspace{-0.3em}   % reduce space above
            \begin{center}
            \rule{0.5\linewidth}{0.4pt}  % half-width line
            \end{center}
        \vspace{-0.3em}   % reduce space below
        
        \textit{ Cargo Volume measurement for an airline (Docker, Python, C++, Open3D, Qt, Depth Cameras - Helios \& Nerion)}
            \begin{itemize}
                \item Multi-process real-time pipe \& filter architecture for 3D Reconstruction, pointcloud cleaning and contour fitting.
            \end{itemize}
        \textit{ Anonymization Software (FastAPI, Milestone VMS, AI Bridge, Pytorch, Tensorrt, PyNvVideoCodec, C++) }
            \begin{itemize}
                \item Implement low-latency face and license plate detection software to anonymize RTSP streams.
                \item Improved load balancing to ensure high GPU utilization using shared decoders and batching.
            \end{itemize}
        \end{cvsubsection}

            \begin{cvsubsection}{Work Student}{Terraloupe \& ECR Gmbh}{April 2018 -- August 2021}
        \textit{Improving Core ML Products and Production Infrastructure (Python, Go, Docker, Kubernetes)}
            \begin{itemize}
                \item Implement serving and testing of PyTorch models over Kubernetes pods.
                \item Implement tracking metrics to benchmark multi-object tracking associators.
                \item Designed benchmark to evaluate internal defect predictors on real data as well as synthetically introduced defects.
                \item Designed 4 new safety performance indicators to measure safety of autonomous vehicles.
            \end{itemize}
            \textit{Training Data Management Tool (Python, Django, PostgreSQL, PostGIS)}
            \begin{itemize}
                \item Development of PostgreSQL-based inventory database with geo-coordinate support for world map datasets and a query service for sampling datasets from the database.
            \end{itemize}
            \textit{Core Deep Learning Pipeline (Docker, Python, Keras, Tensorflow)}
            \begin{itemize}
                \item Development of single pipeline supporting Image Classification, Object Detection and Semantic segmentation tasks.
                \item Optimization of training and inference phase with resulting GPU utilization of over $90\%$.
            \end{itemize}
        \end{cvsubsection}
        
        \begin{cvsubsection}{Image Team Lead}{Roposo, India}{Nov 2015 -- Oct 2017}        
        \textit{Image Processing Service Development (Java, AWS, OpenCV, ffmpeg)}
            \begin{itemize}
                \item Optimizations to efficiently use servers, leading to 70\% cost reduction.
                \item Enable dynamic compression of media using SSIM metric.
                \item Quantifying social posts ownership by measuring plagiarism using image metadata analysis.
                \item Implemented Beauty filter based on variational approach by Farbman, Zeev, et al. \cite{farbman2008edge}
            \end{itemize}
        \end{cvsubsection}
          
        \begin{cvsubsection}{Software Development Engineer}{Amazon, India}{Oct 2014 -- Nov 2015}        
        \textit{Resell Product Form (Java, DynamoDB)}
            \begin{itemize}
                \item Development of data model to reduce user interaction for form completion and data payload for mobile usage.
                \item Improved form completion rate by 5\times with reduction of data payload by 99.5\%.
            \end{itemize}
            
        \textit{Catalog Labeling Quality Platform (Python, Apache Spark)}
            \begin{itemize}
            \item Developed a platform to cluster Amazon catalog data with Human-in-the-Loop analysis, reducing catalog quality check time from several weeks (previously infeasible) to under an hour.
           \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Software Development Engineer}{KritiKal Solutions Pvt. Ltd., India}{June 2012 -- Oct 2014}
            \textit{Atmosphere Turbulence Removal Module (C++, Cuda, DLib, OpenCV, Qt, libpthread)}
            \begin{itemize}
                \item Development of Atmosphere Turbulence Removal Module based on Non-Rigid Registration method \cite{rueckert1999nonrigid}.
                \item Optimizations added using Pipe-And-Filter architecture and cuda implementation, achieving \textbf{240x} speedup.
            \end{itemize}
            
            \textit{Wide Area Tracking Module (C++, OpenCV, Qt)}
            \begin{itemize}
                \item Designed and implemented a module for controlling Pan and Tilt Device.
                \item Real time stitching of multiple CCD/Infrared Cameras to produce a wider view.
                \item Change Detection and Tracking module to detect and track objects of interest.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    
        % academic projects
    \begin{cvsection}[\faFlask]{Academic Projects}
    \begin{cvsubsection}[2]{Master Thesis}{CAMP\footnote{\href{http://campar.in.tum.de/Chair/ResearchIssueComputerVision}{http://campar.in.tum.de/Chair/ResearchIssueComputerVision}}, Technical University of Munich}{Dec 2020 -- June 2021}
    \textit{Weakly Supervised Semantic Segmentation using Low-level neural network features}
        \begin{itemize}
            \item We proposed a novel approach for dissecting classification neural networks to extract semantic maps.
            \item The method improves the mIOU metric by more than 20\% on the vgg and resnet backbone models w.r.t. class activation maps.
        \end{itemize}
    \end{cvsubsection}
    
    \begin{cvsubsection}{Research Assistance Project}{Technical University of Munich}{Dec 2019 -- May 2020}
    \textit{Neural Response Interpretation through the Lens of Critical Paths, CVPR 2021 (Pytorch, python) \cite{khakzar-2021}}
        \begin{itemize}
        \item \textbf{CVPR 2021} - Improving interpretability using path selection via neurons’ contributions to the response.
        \end{itemize}
    \end{cvsubsection}
    
    \end{cvsection}

    \begin{cvsection}[\faGraduationCap]{Education}
        \begin{cvsubsection}{Munich, Germany}{Technical University of Munich}{Oct 2017 -- July 2021}
            \begin{itemize}
                \item M.Sc. in Informatics with \textit{Distinction}, GPA: 1.3/1.0
                \item Graduate Coursework: Machine Learning; Deep Learning; Principles of Computer Vision; Multiple View Geometry; Tracking and Detection in Computer Vision; 3D Scanning \& Motion Capture;  Protein Prediction.
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Dhanbad, India}{Indian Institute of Technology}{July 2008 -- May 2012}
            \begin{itemize}
                \item B.Tech. in Computer Science and Engineering,  CGPA: 7.51/10.0
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    
    \begin{cvsection}[\faTools]{Technical Skills}
        \begin{cvsubsection}{}{}{}    
            \begin{itemize}
                \item Programming Languages: Python, C, C++ with minor dabbles in Go, Matlab, HTML, CSS, JS.
                \item ML/CV Toolkits: PyTorch, OpenCV, Open3D, Numpy, Pandas and many more.
                \item Application Development: Docker, Kubernetes, Rabbitmq, Redis, Kafka, Telegraf, Grafana, Celery, Ansible, Terraform, PyQT, MongoDB, PostgreSQL, InfluxDB.
                \item Project and Team Management - Jira, Linear.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    
    % \begin{cvsection}{Additional Experience and Awards}
    %     \begin{cvsubsection}{}{}{}    
    %         \begin{itemize}
    %             \item Achieved All India rank 1159 in All India Engineering Entrance Exam, 2008 out of 950,000 participants.
    %             \item Open source contributions: \textbf{Open3D}, torchvision, metadata-extractor and imantics\footnote{\href{https://resume.github.io/?saurabheights}{https://resume.github.io/?saurabheights}}, RF-DETR Plugin for Fifty-One.
    %         \end{itemize}
    %     \end{cvsubsection}
    % \end{cvsection}
        \begin{cvsection}[\faScroll]{References}

         \printbibliography[heading=none]

    \end{cvsection}
    
\end{document}
